```{r}
library(edgeR)
```

```{r}
CountTable <- read.csv("kal2.csv", header=TRUE, row.names=1)
dgList <- DGEList(counts=CountTable, genes=rownames(CountTable))
isexpr <- rowSums(cpm(dgList) > 1) >=3 # require a minimum counts per million
#isexpr <- rowSums(dgList$counts > 30) >=6 # or we can specify a minimum count
sum(isexpr)/nrow(dgList)
countsPerMillion <- cpm(dgList)
countCheck <- countsPerMillion > 1
keep <- which(rowSums(countCheck) >= 2)
dgList <- dgList[keep,]
#dgList <- calcNormFactors(dgList, method="TMM")
plotMDS(dgList)
```

```{r}
samples <- read.table("sample.txt", header=TRUE)
batch <- factor(samples$batch)
cond <- factor(samples$condition, levels=c("Ctrl","siRNA"))
#sampleType<- rep("Ctrl", ncol(dgList))
#sampleType[grep("siRNA", colnames(dgList))] <- "siRNA"
#sampleReplicate <- paste("S", rep(1:3, each=2), sep="")
#designMat <- model.matrix(~sampleReplicate + sampleType)
#sampleType
design <- model.matrix(~batch+cond)
y <- estimateDisp(dgList,design)
fit <- glmQLFit(y, design)
qlf <- glmQLFTest(fit)
#ttags = topTags(qlf)
```

```{r}
pval = 0.05

e_df_qlf<-as.data.frame(`qlf`)
e_df_qlf$log10.pvalue<-(-1*log10(e_df_qlf$PValue))
e_df_qlf$Significant.Gene<-"No"
row_number<-which(e_df_qlf$PValue<pval & abs(e_df_qlf$logFC)>1)
e_df_qlf$Significant.Gene[row_number]<-"Yes"

e_df_qlf$Differential_Gene<-e_df_qlf$Significant.Gene
e_df_qlf$Differential_Gene[which(e_df_qlf$PValue< pval & e_df_qlf$logFC> 1)]<-"Up-Regulated"
e_df_qlf$Differential_Gene[which(e_df_qlf$PValue< pval & e_df_qlf$logFC< -1)]<-"Down-Regulated"

sub_e_qlf = subset(e_df_qlf, abs(e_df_qlf$logFC) > 1 & e_df_qlf$PValue < pval)
write.csv(sub_e_qlf, "sub_e_qlf.csv", row.names=TRUE)
write.csv(e_df_qlf, "e_df_qlf.csv", row.names=TRUE)
```

```{r Volcano plot with ggplot2}
library(ggplot2)
library(ggrepel)
#RNA volcano

#make sure to adjust xlim and ylim based off of the data. Run hist(e_df_qlf$logFC) and hist(e_df_qlf$log10.pvalue) to get an idea

# pick a set of genes to label:
e_df_qlf$label<-"No"
e_df_qlf$label[which(e_df_qlf$PValue<0.05 & abs(e_df_qlf$logFC)>1)]<-"Yes"

# Here we add two further columns, the gene symbol (common name) and entrez ID - both of which may be useful downstream
e_df_qlf$symbol <- mapIds(org.Hs.eg.db, keys=row.names(e_df_qlf), column="SYMBOL", keytype="ENSEMBL", multiVals="first") # MAPS GENE IDs
e_df_qlf$entrez <- mapIds(org.Hs.eg.db, keys=row.names(e_df_qlf), column="ENTREZID", keytype="ENSEMBL", multiVals="first")

#pdf("Volcano.pdf", width=8, height=4,useDingbats=FALSE)
pRNA <- ggplot(e_df_qlf, aes(logFC, log10.pvalue))+
  geom_point(aes(colour = Differential_Gene),size=1)+
  scale_colour_manual(values=c("blue", "black","red"))+
  xlim(-6,6)+
  ylim(0,5)+
  xlab(expression(paste(log[2], 'FC(Ctrl/siRNA)')))+
  ylab(expression(paste(-log[10], '(Q-value)'))) +
  theme_bw() + 
  theme(panel.background = element_blank())+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))+

  theme(text = element_text(size=10)) +
  theme(plot.title = element_blank())+
  theme(axis.text = element_text( color = "black", size = 10))+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), axis.line=element_line()) +
  theme(legend.position="none")+
  geom_vline(xintercept=-abs_log2fc,linetype="dotted")+
  geom_vline(xintercept=abs_log2fc,linetype="dotted")+
  geom_text_repel(
    data = subset(e_df_qlf, label=="Yes"),
    aes(label = e_df_qlf$symbol[which(label=="Yes")]),
    size = 5,
    box.padding = unit(0.35, "lines"),
    point.padding = unit(0.5, "lines")
  )
pRNA
